---
title: "sample_hansard"
author: "Steph Buongiorno"
date: "6/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(tidyverse)

hansard <- fread("/scratch/group/pract-txt-mine/hansard_justnine_12192019.csv") %>%
  select(sentence_id, text)
```

##Interrogative Sentences and Sentences with “Wh-” Fronting
Interrogative sentences are sentences that ask a question and are punctuated with a question mark. As mentioned earlier, subjects generally precede the verb or object in an English sentence. An exception is when asking a question. Questions are often structured by “wh-” fronting, where the object is transposed in front of the subject. Consider the following sentence:

“Which car did you say that Mary wanted to buy?”

In this example, the object “car” comes before the subject “Mary” and the verb “wanted.”

```{r}
which_what <- hansard %>%
  filter(str_detect(text, regex("^Which (.*)\\?$|^What (.*)\\?$")), 
         !str_detect(text, regex("hon\\.$")),
         nchar(text) > 40) %>%
  sample_n(1000)

write_csv(which_what, "~/placeholder_3.csv")

hansard_sample <- read_csv("")

incomplete_or_incorrect_sentences <- c("S3V0110P0_17033", "S3V0326P0_11946", "S4V0010P0_22877", "S4V0081P0_800")

for(id in incomplete_or_incorrect_sentences) {
  
  which_what <- which_what %>%
    filter(!str_detect(sentence_id, regex(id))) }

replace <- (1000 - nrow(which_what))
if(replace != 0) {
  replace_ww <- which_what %>%
    sample_n(replace)
  
  which_what <- bind_rows(which_what, replace_ww) }
```

##Sentences with Leftward Syntactic Movement (without “wh-” fronting)
Leftward syntactic movement occurs when an object or verb precedes a subject. English is considered a rigid “subject-verb-object” language, meaning that within a sentence, the subject usually comes first followed by the verb and then the object. However, sometimes grammatical sentences will feature the verb or object preceding the subject. Consider the following sentence:

“After watching it like 5 or 6 times, I think I see what happened.”

In this example, the verb “watching” and the object “it” come before the subject “I.”

```{r}
after <- hansard %>%
  filter(str_detect(text, regex("^After ")), 
         !str_detect(sentence_id, regex("hon\\.$")),
         nchar(text) > 40) %>%
  sample_n(1000)

write_csv(sample_which_what, "~/placeholder_4.csv")

hansard_sample <- read_csv("")

incomplete_or_incorrect_sentences <- c("", "", "", "")

for(id in incomplete_or_incorrect_sentences) {
  
  after <- after %>%
    filter(!str_detect(sentence_id, regex(id))) }

replace <- (1000 - nrow(after))
if(replace != 0) {
  replace_a <- after %>%
    sample_n(replace)
  
  after <- bind_rows(after, replace) }
```

##Sentences Selected at Random
Random sentences are sentences drawn without any manual intervention. They include simple sentences (e.g. sentences composed of a single, independent clause) to compound-complex sentences (e.g. sentences with multiple, dependent clauses).

```{r}
hansard_sample <- hansard %>%
  sample_n(2000) %>%
  filter(!str_detect(text, regex("hon\\.$")),
         !str_detect(text, regex("^(?![A-Z])"))) %>%
  filter(str_count(text, "\\w+") > 4) %>%
  sample_n(1000)

write_csv(hansard_sample, "~/placeholder_5.csv")

hansard_sample <- read_csv("")

incomplete_or_incorrect_sentences <- c("", "", "", "")

for(id in incomplete_or_incorrect_sentences) {
  
  hansard_sample <- hansard_sample %>%
    filter(!str_detect(sentence_id, regex(id))) }

replace <- (1000 - nrow(hansard_sample))
if(replace != 0) {
  replace_a <- hansard_sample %>%
    sample_n(replace)
  
  after <- bind_rows(after, replace) }

```

##Compound Sentences, Complex Sentences, and Compound-Complex Sentences
Compound sentences are sentences where two or more independent clauses are joined together with a coordinating conjunction such as “for” or “yet,” or a conjunctive adverb such as “however.” Complex sentences are sentences that have one independent clause and one or more subordinate clauses that modify the main subject or verb of a sentence. Compound-complex sentences are sentences that contain at least three clauses: two independent clauses and one or more dependent clauses. In total, a compound-complex sentence can have three or more sets of subject-verb relations.

```{r}
compound_complex_compoundcomplex <- hansard %>%
  sample_n(100000) %>%
  filter(!str_detect(text, regex("hon\\.$")),
         !str_detect(text, regex("^(?![A-Z])")),
         str_detect(text, regex(" and,| but,| or,"))) %>%
  sample_n(1000)

write_csv(hansard_sample, "~/placeholder_6.csv")

hansard_sample <- read_csv("")

incomplete_or_incorrect_sentences <- c("", "", "", "")

for(id in incomplete_or_incorrect_sentences) {
  
  hansard_sample <- hansard_sample %>%
    filter(!str_detect(sentence_id, regex(id))) }

replace <- (1000 - nrow(hansard_sample))
if(replace != 0) {
  replace_a <- hansard_sample %>%
    sample_n(replace)
  
  after <- bind_rows(after, replace) }
```



